
---
title: "Mixed Effects Model Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document demonstrates how to analyze a dataset using mixed-effects models. The dataset contains repeated measures of participant performance over time, with varying task difficulty levels. Mixed-effects models are used to account for both fixed effects (e.g., task difficulty) and random effects (e.g., individual differences).

---

## Step 1: Load the Data

```{r load-data}
# Load necessary libraries
library(tidyverse)
library(lme4)

# Load the dataset (assuming it's in the same folder as this Rmd file)
data <- read.csv("mixed_effects_data.csv")

# Quick look at the data
head(data)
summary(data)
```

---

## Step 2: Visualize the Data

```{r visualize-data}
# Plot performance over time for all participants
ggplot(data, aes(x = Time, y = Performance, group = Participant_ID)) +
  geom_line(alpha = 0.5) +
  labs(title = "Performance Over Time by Participant", x = "Time", y = "Performance")

# Plot average performance over time
ggplot(data, aes(x = Time, y = Performance)) +
  stat_summary(fun = mean, geom = "line", color = "blue", size = 1.2) +
  labs(title = "Average Performance Over Time", x = "Time", y = "Average Performance")
```

---

## Step 3: Fit a Mixed Effects Model

```{r fit-mixed-model}
# Fit a mixed-effects model
mixed_model <- lmer(Performance ~ Difficulty + (1 + Time | Participant_ID), data = data)

# Summary of the model
summary(mixed_model)
```

---

## Step 4: Interpret the Results

```{r interpret-results}
# Fixed effects
cat("Fixed Effects:
")
print(fixef(mixed_model))

# Random effects
cat("
Random Effects:
")
print(ranef(mixed_model))

# Model diagnostics
plot(mixed_model)
```

---

## Conclusion

This document demonstrates the use of mixed-effects models to analyze repeated measures data. The model accounts for both fixed effects (e.g., task difficulty) and random effects (e.g., individual differences in intercepts and slopes). You can extend this workflow to more complex datasets or research questions.

